---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

### install.packages('pkgnet');
```

# yum: YAML Utilities & More

The goal of `yum` is to provide a number of functions to work with files that contain one or more YAML fragments. Several packages leverage the YAML format to facilitate systematic encoding of information in a format that is both machine- and human-readable. The yum package provides a number of functions to facilitate this in a uniform manner with minimal dependencies (i.e. only suggests [yaml::yaml] and [data.tree::data.tree] to enable additional functionality).

<!-- [![CRAN status](https://www.r-pkg.org/badges/version/yum)](https://cran.r-project.org/package=yum) -->
[![Travis build status](https://travis-ci.org/Matherion/yum.svg?branch=master)](https://travis-ci.org/Matherion/yum)

## Installation

You can install the released version of yum from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("yum");
```

## Dependencies

`yum` was created to have minimal dependencies. However, you will usually want to have either [yaml::yaml] or [data.tree::data.tree] available to be able to actually load (parse) the extracted YAML fragments and organise them in a tree if they have a hierarchical structure. Therefore, `yum` does have some dependencies through those two suggested packages. Of these, `yaml` only has one dependency, but `data.tree` has a few more. Specifically, the dependency network looks like this:

```{r depnet, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=20}

#' Plot network of package dependencies
#'
#' @param pkg package description, can be path or package name. See \code{\link[devtools]{as.package}} for
#'    more information.
#'
#' @details The resulting plot visualizes the network of package dependencies. If you are trying to cut down
#'    on package dependencies look for big red dots that represent a lot of upstream but few downstream
#'    dependencies.
#' @import ggplot2
#' @export
#'
#' @examples

### From https://gist.githubusercontent.com/crsh/c906e93c260488e7363ea606243057c2/raw/f6f0fce38bc274446d205854ea35cfa03b9b1f7a/plot_dependencies.R
### Which I found at https://github.com/crsh/papaja/blob/master/README.Rmd
### Adjusted a bit to enable working with suggestions only
# install.packages("intergraph");

plot_dependencies <- function(pkg = ".") {
  
  library("devtools")
  library("miniCRAN")
  library("igraph")
  library("ggplot2")
  library("ggnetwork")
  
  pkg <- devtools::as.package(pkg)
  
  ### Start of adjustments
  if (is.null(pkg$imports)) {
    dependencies <- unlist(strsplit(pkg$suggests, split = "\n"))
  } else {
    dependencies <- unlist(strsplit(pkg$imports, split = "\n"))[-1]
  }
  ### End of adjustments
  
  dependencies <-
    gsub("\\n| \\(.+\\)|,", "", dependencies)
  dependency_graph <-
    miniCRAN::makeDepGraph(dependencies, suggests = TRUE, enhances = FALSE)
    #miniCRAN::makeDepGraph(dependencies, suggests = FALSE, enhances = FALSE)
  class(dependency_graph) <-
    "igraph"
  dependency_graph <-
    dependency_graph +
    igraph::vertices(pkg$package) +
    igraph::edges(as.vector(rbind(dependencies, pkg$package)))
  dependency_graph <- igraph::simplify(dependency_graph)
  
  edge_list <- igraph::get.edgelist(dependency_graph)
  dependency_graph <- igraph::graph(rbind(edge_list[, 2], edge_list[, 1]))
  
  dependency_graph_df <- ggnetwork::ggnetwork(
    dependency_graph
    , layout = "fruchtermanreingold"
    , arrow.gap = 0.015
    , layout.par = list(niter = 5000)
  )
  
  dependency_graph_df$package <- dependency_graph_df$vertex.names
  dependency_graph_df$face <- ifelse(dependency_graph_df$package == pkg$package, "bold", "plain")
  
  dependency_graph_df$n_dependencies <- as.vector(table(gsub("\\|.+", "", attr(igraph::E(dependency_graph), "vnames")))[as.character(dependency_graph_df$package)])
  dependency_graph_df$n_dependencies[is.na(dependency_graph_df$n_dependencies)] <- 0
  
  dependency_graph_df$importance <- as.vector(table(gsub(".+\\|", "", attr(E(dependency_graph), "vnames")))[as.character(dependency_graph_df$package)])
  dependency_graph_df$importance[is.na(dependency_graph_df$importance)] <- 0
  
  max_downstream_deps <- max(dependency_graph_df$importance)
  
  dependency_graph_df$importance <- dependency_graph_df$importance / max_downstream_deps
  dependency_graph_df$importance <- abs(1 - dependency_graph_df$importance)
  
  dependency_graph_df <- as.data.frame(lapply(dependency_graph_df, as.vector))
  
  ggplot(dependency_graph_df, aes(x = x, y = y, xend = xend, yend = yend)) +
    geom_nodes(aes(color = n_dependencies), size = 6.5, alpha = 0.4) +
    geom_edges(arrow = arrow(length = unit(4, "pt"), type = "closed"), color = grey(0.4)) +
    geom_nodelabel_repel(
      aes(label = package, fontface = face, color = n_dependencies)
      , box.padding = unit(8, "pt")
    ) +
    geom_nodes(aes(color = n_dependencies, size = 7 * importance)) +
    scale_color_distiller(palette = "Spectral") +
    scale_size(labels = function(x) abs(max_downstream_deps - ceiling(x / 7 * max_downstream_deps))) +
    theme_blank(legend.position = "top") +
    guides(
      size = guide_legend(title = "Downstream dependencies", title.position = "top", title.hjust = 0.5, label.position = "bottom", label.hjust = 0.5)
      , color = guide_colorbar(title = "Upstream dependencies", title.position = "top", title.hjust = 0.5, barwidth = unit(130, "pt"), barheight = unit(4, "pt"))
    )
}

plot_dependencies();

### Doesn't seem to enable easy generation of the network alone
# yumReport <-
#   pkgnet::CreatePackageReport(pkg_name = "yum",
#                               pkg_reporters=list(pkgnet::SummaryReporter(),
#                                                  pkgnet::FunctionReporter(),
#                                                  pkgnet::DependencyReporter$new(c('Imports', 'Depends', 'Suggests'))));

```
